% This is a LaTeX template for homework solving, intended to be: 

% 1. Easy to use;
% 2. Elegant;
% 3. Self-explanatory.

% It was written by Lucas R. Ximenes (Jimeens)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{solutionclass} % I wrote the design using a4paper, 11pt, twoside, but feel free to change in solutionclass.cls file (line 4)

\pagestyle{plain}

\begin{document}

\pretitle
{Architectural Recovery}               % ⟸ Write your main Title here
{Software Architecture}        % ⟸ Write your subtitle here
{Frederik Gantriis Møller}                 % ⟸ Write your name here

% Change your homework number here
\def\homeworkNumber{5}

\makeatletter
    \startcontents[sections]
    \phantomsection
    \chapter{Introduction}
\makeatother

What is the problem?
What is the system? 

\section{Methodology}
Tool support: did you use any off-the shelf tools? Your own scripts? Adapt the ones in the course?

Data gathering: what sources of data did you use? Source viewpoints? Reverse engineering patterns? 

Knowledge inference: did you use any abstraction approach? What target viewpoint do you want to recover? 

\section{Results}
The most relevant architectural views (one to three at most) that you recovered from the analysis of the system
Explain the elements in the architectural view(s)

\section{Discussion} 
[optional] Recommendations for reengineering of the system (did you discover things that seem wrong and should be corrected?)
What are the limitations of your approach 
What would you do better if you had more time

\section{Appendix}
Brief description of your code and link to GH repository or Collab notebook
Time allocation: how did you spend your time
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Add these commands below if it's not a problem for you 
    \thispagestyle{fancyplain}
    \fancyhead{}
    \renewcommand{\headrulewidth}{0pt}
    \rfoot{Template by L. R. Ximenes (Jimeens)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}
